\documentclass{article}

\usepackage[margin=0.5in]{geometry}

\title{Problem Set 3}
\author{Mark Xavier (xaviem01)}

\begin{document}
	\maketitle
	
	\begin{enumerate}
		
		%% Problem 1
		\item Constraint 1: Any set $W_i \in W$ where $W_i$ is also in $Y$, the union of all such $W_i$ should include any atom of $U$ exactly once.  In other words, $\forall a \in U,$ if $a \in Y$ then it is only in $Y$ once.
		
		Constraint 2: For the problem to actually be satisfiable, the union of all sets $W_i \in W$ must include every $a \in U$ \textbf{at least once}.  If this constraint is not met, the problem is unsatisfiable as no collection of $W_i$ will include every atom in $S$.
		
		%% Problem 2
		\item Problem 2:
			
			\begin{enumerate}
				
				%% 2a
				\item {\tt Parent(Anne, Ted)}
				
				%% 2b
				\item $\forall_{x, y} \phantom{a} {\tt Parent(x, y) \Rightarrow Earlier(Birth(p), Birth(q))}$
				
				%% 2c
				\item $\forall_{p,q}, {\tt Living(p, t) \Leftrightarrow Earlier(Birth(p), t) \wedge Earlier(t, Death(p))}$
				
				%% 2d
				\item $\forall_{ta, tb} \phantom{a} {\tt Earlier(ta,tb) \Rightarrow \neg Earlier(tb,ta)}$ (I use implies instead of iff to account for the case where ta == tb)
				
				%% 2e
				\item $\forall_{ta,tb,tc} \phantom{a} {\tt Earlier(ta,tb) \wedge Earlier(tb, tc) \Rightarrow Earlier(ta, tc)}$
				
				%% 2f
				\item $\forall_p \phantom{a} \exists_t \phantom{a} {\tt s.t. Living(p,t)}$
				
				%% 2g
				\item ${\tt \neg Living(Ted, Born(Anne))}$
				
				%% 2h
				\item $\forall_p \phantom{a} {\tt Earlier(Born(p), Death(p))}$
				 
			\end{enumerate}
		
		%% Problem 3
		\item After conversion to CNF, we are left with the following clauses:
		
		a.\phantom{1} {\tt Parent(Anne, Ted)}\\
		b.\phantom{1} ${\tt \neg Parent(x,y) \vee Earlier(Birth(x), Birth(y))}$\\
		c1. ${\tt \neg Living(p,t) \vee Earlier(Birth(p), t)}$\\
		c2. ${\tt \neg Living(p,t) \vee Earlier(t, Death(p))}$\\
		c3. ${\tt \neg Earlier(Birth(p),t) \vee \neg Earlier(t, Death(p)) \vee Living(p,t)}$\\
		d.\phantom{1} ${\tt \neg Earlier(ta, tb) \vee \neg Earlier(tb, ta)}$
		
		Now assume {\tt Living(Ted, Born(Anne))}.  Given (a), we know {\tt Earlier(Birth(Anne), Birth(Ted))}.  Then we know from (c1) that for {\tt Living(Ted, Born(Anne)) we need Earlier(Birth(Ted), Birth(Anne))}.\\  This leads to {\tt Earlier(Birth(Anne), Birth(Ted))} from (a), but also {\tt Earlier(Birth(Ted), Birth(Anne))} from (c1), and per (d), we have a contradiction.  Therefore we prove by contradiction that {\tt $\neg$ Living(Ted, Born(Anne))}.
		
		%% Problem 4
		\item After conversion to CNF, we are left with the following clauses:
		
		c1. ${\tt \neg Living(p,t) \vee Earlier(Birth(p), t)}$\\
		c2. ${\tt \neg Living(p,t) \vee Earlier(t, Death(p))}$\\
		c3. ${\tt \neg Earlier(Birth(p),t) \vee \neg Earlier(t, Death(p)) \vee Living(p,t)}$\\
		e.\phantom{1} ${\tt \neg Earlier(ta, tb) \vee \neg Earlier(tb, tc) \vee Earlier(ta, tc)}$\\
		f.\phantom{1} ${\tt Living(p, \lambda(p))}$
		
		Now assume ${\tt \neg Earlier(Born(p), Death(p))}$.  Then from (f), we have that $p$ is living at time $\lambda(p)$.  From (c1), we have {\tt Earlier(Birth(p), $\lambda(p)$)} and (c2) gives {\tt Earlier($\lambda(p)$, Death(p))}.  However, at (e), we get that {\tt Earlier(Birth(p), $\lambda(p)$) $\wedge$ Earlier($\lambda(p)$, Death(p))} leads to {\tt Earlier(Birth(p), Death(p))}.  However, this is in direct contradiction to our starting assumption, meaning our assumption was wrong and (h) is proven.
		 
	\end{enumerate}
\end{document}